IFA Comparison of Noncognitive Skills \\ BCS and MCS

### 2018-04-25 codes/R/paper/cohorts_nc.Rnw
add mini table of quantile income differences

>>>>

<<INCINEQ_STATS, dependson="FA_SCORES_MAIN", results="markup">>=
tb <- data.frame(
  aggregate(scores2plot$faminc_infl, by=list(scores2plot$cohort), FUN = function(x) quantile(x, c(.1, .25, .75, .9), na.rm=T))
)
tb$d9010 <- tb$x[,4]/tb$x[,1]
tb$d7525 <- tb$x[,3]/tb$x[,2]

cat("Quantile differences in income by cohort")
tb
@
